MIRSVM: Multi-Instance Support Vector Machine with Bag Representatives

### 2017-07-13 ArticleRevision/article/article.tex
Integrated new stats into article

The Nemenyi, Holm, and Shaffer post-hoc~\citep{Gibbons2011,Holander1999} tests were then run for each of the metrics to compute multiple pairwise comparisons between the proposed algorithm and the state-of-the-art methods, investigating whether statistical differences exist among pairs of algorithms. Tables~\ref{tab:statacc},~\ref{tab:statprec},~\ref{tab:statrec},~\ref{tab:statkappa}, and~\ref{tab:statauc} show the $p$-values for the Nemenyi, Holm, and Shaffer tests for $\alpha = 0.05$.
\newpage
\subsection{Accuracy}
\begin{table}[t!]
\caption{Accuracy}\label{tab:accResults}
\resizebox{0.95\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}ccccccccccccc}
\noalign{\smallskip}\hline\noalign{\smallskip}
Datasets &MIRSVM & miGraph & MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
\noalign{\smallskip}\hline\noalign{\smallskip}
suramin &0.7000 &\textbf{0.8462} &0.5000 &0.7250 &0.4250 &0.5000 &0.7250 &0.5000 &0.5000 &0.6000 &0.6650 &0.4615 &  \\
eastWest &\textbf{0.8000} &0.7000 &0.5000 &0.7250 &0.6125 &0.5000 &0.7125 &0.5625 &0.5000 &0.6000 &0.6000 &0.4500 &  \\
westEast &0.7000 &0.7500 &0.5000 &0.3750 &0.4500 &0.5000 &0.7375 &0.4125 &0.5000 &0.5625 &\textbf{0.9649} &0.6375 &  \\
musk1 &\textbf{0.9022} &0.8152 &0.5109 &0.7717 &0.8804 &0.5109 &0.7826 &0.7609 &0.5109 &0.8587 &0.8142 &0.8587 &  \\
musk2 &0.8218 &0.7426 &0.6139 &0.7723 &0.7228 &0.6139 &0.7030 &0.7129 &0.6139 &0.6238 &\textbf{0.8756} &0.6733 &  \\
webmining &0.8500 &0.8142 &0.8142 &0.7699 &0.8142 &0.8142 &0.8407 &0.6903 &0.8142 &0.8142 &\textbf{0.9358} &0.8053 &  \\
trx &0.8825 &0.8964 &0.8705 &\textbf{0.9016} &0.8808 &0.8705 &0.8705 &0.8705 &0.8705 &0.8756 &0.6450 &0.8860 &  \\
mutagenesis-atoms &0.7714 &0.7606 &0.6649 &0.6436 &0.7074 &0.6649 &0.6915 &0.6649 &0.6649 &\textbf{0.7766} &\textbf{0.7766} &0.7606 &  \\
mutagenesis-bonds &0.8252 &0.7872 &0.6649 &0.6915 &0.7713 &0.6649 &0.7979 &0.6649 &0.6649 &0.8351 &0.8351 &\textbf{0.8564} &  \\
mutagenesis-chains &\textbf{0.8411} &0.7926 &0.6649 &0.6702 &0.7766 &0.6649 &0.8351 &0.6649 &0.6649 &0.8404 &0.8404 &0.8351 &  \\
tiger &0.7750 &0.7950 &0.5000 &0.5000 &0.7100 &0.5000 &0.7200 &0.7550 &0.5000 &0.6650 &\textbf{0.8000} &0.7250 &  \\
elephant &\textbf{0.8300} &\textbf{0.8300} &0.5000 &0.5000 &0.7900 &0.5000 &0.8100 &0.8000 &0.5000 &0.8000 &0.5625 &0.8250 &  \\
fox &0.6550 &0.6300 &0.5000 &0.5000 &0.5800 &0.5000 &0.5250 &0.4750 &0.5000 &0.6450 &\textbf{0.8587} &0.6500 &  \\
component &\textbf{0.9366} &0.9153 &0.8649 &0.8696 &0.8780 &0.8649 &0.8968 &0.8703 &0.8649 &0.9358 &0.6000 &0.9355 &  \\
function &0.9523 &0.9405 &0.9155 &0.9138 &0.9193 &0.9155 &0.9376 &0.9195 &0.9155 &\textbf{0.9649} &0.6238 &0.9647 &  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Average &\textbf{0.8162} &0.8010 &0.6390 &0.6886 &0.7279 &0.6390 &0.7724 &0.6883 &0.6390 &0.7598 &0.7598 &0.7550 &  \\
Rank &\textbf{2.4333} &3.8333 &9.6000 &7.8000 &6.5667 &9.6000 &5.2000 &8.5667 &9.6000 &4.7000 &4.8667 &5.2333 &  \\
\noalign{\smallskip}\hline
\end{tabular}}
\centering
\resizebox{0.95\textwidth}{!}{\begin{tikzpicture}
\draw (1,0) -- (11,0);
\foreach \x in {1,2,3,4,5,6,7,8,9,10,11} {
\draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
\ifthenelse{\x < 11}{\draw (\x+.5, 0) -- ++(0,.03);}{}
}
\coordinate (c0) at (2.4333,0);
\coordinate (c1) at (3.8333,0);
\coordinate (c2) at (9.6,0);
\coordinate (c3) at (7.8,0);
\coordinate (c4) at (6.5667,0);
\coordinate (c5) at (9.6,0);
\coordinate (c6) at (5.2,0);
\coordinate (c7) at (8.5667,0);
\coordinate (c8) at (9.6,0);
\coordinate (c9) at (4.7,0);
\coordinate (c10) at (4.8667,0);
\coordinate (c11) at (5.2333,0);

\node (l0) at (c0) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
\node (l1) at (c1) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
\node (l2) at (c2) [above left=.22cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
\node (l3) at (c3) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
\node (l4) at (c4) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
\node (l5) at (c5) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
\node (l6) at (c6) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
\node (l7) at (c7) [above left=.22cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
\node (l8) at (c8) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
\node (l9) at (c9) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
\node (l10) at (c10) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
\node (l11) at (c11) [above left=.2cm and 0cm, align=right,scale=0.7] {\tiny Stacking};

\fill[fill=gray,fill opacity=0.5] (2.4333,-0.1) rectangle (5.8733,0.1);

\foreach \x in {0,1,2,3,4,5,6,7,8,9,10,11} {
\draw (l\x) -| (c\x);
};
\end{tikzpicture}}\vspace{-0.6em}
\captionof{figure}{Bonferroni-Dunn test for Accuracy}\label{fig:BonfDunnacc}\vspace{-0.5em}
\captionof{table}{Nemenyi, Holm, and Shaffer tests for Accuracy}\label{tab:statacc}
\scriptsize
\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
MIRSVM vs. &miGraph &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging& Stacking \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Nemenyi $p$-value &0.9961 &0.0000 &0.0027 &0.0734 &0.0000 &0.6218 &0.0002 &0.0000 &0.8586 &0.7910 &0.6034 &  \\
Holm $p$-value &1.0000 &0.0000 &0.0188 &0.4405 &0.0000 &1.0000 &0.0016 &0.0000 &1.0000 &1.0000 &1.0000 &  \\
Shaffer $p$-value &0.9961 &0.0002 &0.1207 &1.0000 &0.0002 &1.0000 &0.0090 &0.0002 &1.0000 &1.0000 &1.0000 &  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}}
\end{table}
Table~\ref{tab:accResults} shows the accuracy results of the $11$ algorithms over $15$ multi-instance datasets, along with their average and rank. The results indicate that the bag-based and ensemble learners perform better than the instance-based and wrapper methods. Specifically, MIRSVM achieves the best accuracy over $6$ of the $15$ datasets with a competitive average against the Bagging, Stacking, and TLC algorithms. Note that MIRSVM performs better than MISVM for all datasets, indicating that using representatives from each bag and limiting the number of support-vectors per negative bag improves the classification performance. The instance-level classifiers and wrapper methods, such as MIBoost, MIWrapper, and SimpleMI perform the worst. This behavior emphasizes the importance of not making prior assumptions about the positive bags' distributions.

@@

\begin{table}[H]
\caption{Precision}\label{tab:preResults}
\resizebox{0.95\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}ccccccccccccc}
\noalign{\smallskip}\hline\noalign{\smallskip}
Datasets &MIRSVM & miGraph & MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
\noalign{\smallskip}\hline\noalign{\smallskip}
suramin &0.6383 &0.7778 &\textbf{1.0000} &\textbf{1.0000} &0.2857 &\textbf{1.0000} &\textbf{1.0000} &0.5000 &\textbf{1.0000} &0.6429 &0.6514 &0.4000 &  \\
eastWest &0.7143 &0.7000 &0.5000 &0.8750 &0.5882 &0.5000 &0.7429 &\textbf{1.0000} &0.5000 &0.6053 &0.6053 &0.4444 &  \\
westEast &0.6700 &0.7273 &0.5000 &0.2727 &0.4600 &0.5000 &0.6939 &0.3600 &0.5000 &0.5581 &\textbf{0.9729} &0.6038 &  \\
musk1 &0.8519 &0.7778 &\textbf{1.0000} &0.9286 &0.9048 &\textbf{1.0000} &0.8049 &0.8108 &\textbf{1.0000} &0.8478 &0.8817 &0.8478 &  \\
musk2 &0.7059 &0.7826 &0.6139 &0.7826 &0.7576 &0.6139 &0.7424 &0.7538 &0.6139 &0.7400 &\textbf{0.9138} &0.7164 &  \\
webmining &0.7500 &\textbf{1.0000} &0.8142 &0.8173 &0.8142 &0.8142 &0.8936 &\textbf{1.0000} &0.8142 &0.8817 &0.9462 &0.8500 &  \\
trx &0.6500 &0.8571 &0.8705 &\textbf{0.9306} &0.9191 &0.8705 &0.8705 &0.8705 &0.8705 &0.9138 &0.6747 &0.9011 &  \\
mutagenesis-atoms &0.7872 &0.7985 &\textbf{1.0000} &0.4630 &0.6111 &\textbf{1.0000} &0.5439 &\textbf{1.0000} &\textbf{1.0000} &0.7059 &0.7059 &0.6667 &  \\
mutagenesis-bonds &0.8468 &0.8195 &\textbf{1.0000} &0.5385 &0.7500 &\textbf{1.0000} &0.6812 &\textbf{1.0000} &\textbf{1.0000} &0.7857 &0.7857 &0.8333 &  \\
mutagenesis-chains &0.8571 &0.8116 &\textbf{1.0000} &0.5091 &0.7059 &\textbf{1.0000} &0.7759 &\textbf{1.0000} &\textbf{1.0000} &0.7705 &0.7705 &0.7581 &  \\
tiger &0.7365 &0.7323 &0.5000 &0.5000 &0.6944 &0.5000 &0.7444 &0.7802 &0.5000 &0.6514 &\textbf{0.8000} &0.7320 &  \\
elephant &0.8576 &\textbf{0.8750} &0.5000 &0.5000 &0.7959 &0.5000 &0.8444 &0.7679 &0.5000 &0.8000 &0.5581 &0.8283 &  \\
fox &0.6040 &0.6275 &0.5000 &0.5000 &0.5833 &0.5000 &0.5287 &0.4854 &0.5000 &0.6747 &\textbf{0.8478} &0.6705 &  \\
component &\textbf{0.9866} &0.7782 &0.8649 &0.8778 &0.8902 &0.8649 &0.8958 &0.8696 &0.8649 &0.9462 &0.6429 &0.9449 &  \\
function &0.8459 &0.6775 &0.9155 &0.9202 &0.9317 &0.9155 &0.9376 &0.9197 &0.9155 &\textbf{0.9729} &0.7400 &0.9726 &  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Average &0.7668 &0.7828 &0.7719 &0.6944 &0.7128 &0.7719 &0.7800 &\textbf{0.8079} &0.7719 &0.7665 &0.7665 &0.7447 &  \\
Rank &6.3333 &6.0000 &7.0333 &7.2667 &7.3000 &7.0333 &\textbf{5.7333} &5.8000 &7.0333 &5.7667 &6.2000 &6.5000 &  \\
\noalign{\smallskip}\hline
\end{tabular}}
\centering
\resizebox{0.95\textwidth}{!}{\begin{tikzpicture}
\draw (3,0) -- (12,0);
\foreach \x in {3,4,5,6,7,8,9,10,11,12} {
\draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
\ifthenelse{\x < 12}{\draw (\x+.5, 0) -- ++(0,.03);}{}
}

\coordinate (c0) at (6.3333,0);
\coordinate (c1) at (6,0);
\coordinate (c2) at (7.0333,0);
\coordinate (c3) at (7.2667,0);
\coordinate (c4) at (7.3,0);
\coordinate (c5) at (7.0333,0);
\coordinate (c6) at (5.7333,0);
\coordinate (c7) at (5.8,0);
\coordinate (c8) at (7.0333,0);
\coordinate (c9) at (5.7667,0);
\coordinate (c10) at (6.2,0);
\coordinate (c11) at (6.5,0);

\node (l0) at (c0) [above left=.38cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
\node (l1) at (c1) [below left=.2cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
\node (l2) at (c2) [above right=.23cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
\node (l3) at (c3) [below right=.17cm and 0cm, align=left,scale=0.7] {\tiny MIOptimalBall};
\node (l4) at (c4) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
\node (l5) at (c5) [above right=.35cm and 0cm, align=left,scale=0.7] {\tiny MIWrapper};
\node (l6) at (c6) [above left=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
\node (l7) at (c7) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
\node (l8) at (c8) [above right=.5cm and 0cm, align=left,scale=0.7] {\tiny SimpleMI};
\node (l9) at (c9) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny TLC};
\node (l10) at (c10) [below right=.25cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
\node (l11) at (c11) [below right=.1cm and 0cm, align=right,scale=0.7] {\tiny Stacking};

\fill[fill=gray,fill opacity=0.5] (5.7333,-0.1) rectangle (9.17,0.1);

>>>>

The Nemenyi, Holm, and Shaffer post-hoc~\citep{Gibbons2011,Holander1999} tests were then run for each of the metrics to compute multiple pairwise comparisons between the proposed algorithm and the state-of-the-art methods, investigating whether statistical differences exist among pairs of algorithms. Tables~\ref{tab:statacc},~\ref{tab:statprec},~\ref{tab:statrec},~\ref{tab:statkappa}, and~\ref{tab:statauc} show the $p$-values for the Nemenyi, Holm, and Shaffer tests for $\alpha = 0.05$.
\newpage
\subsection{Accuracy}
\begin{table}[t!]
\caption{Accuracy}\label{tab:accResults}
\resizebox{0.95\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}ccccccccccccc}
\noalign{\smallskip}\hline\noalign{\smallskip}
Datasets &MIRSVM & miGraph & MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
\noalign{\smallskip}\hline\noalign{\smallskip}
suramin &0.8000 &\textbf{0.8462} &0.5000 &0.7250 &0.4250 &0.5000 &0.7250 &0.5000 &0.5000 &0.6000 &0.6650 &0.4615 &  \\
eastWest &\textbf{0.8000} &0.7000 &0.5000 &0.7250 &0.6125 &0.5000 &0.7125 &0.5625 &0.5000 &0.6000 &0.6000 &0.4500 &  \\
westEast &0.7500 &0.7500 &0.5000 &0.3750 &0.4500 &0.5000 &0.7375 &0.4125 &0.5000 &0.5625 &\textbf{0.9649} &0.6375 &  \\
musk1 &\textbf{0.9022} &0.8152 &0.5109 &0.7717 &0.8804 &0.5109 &0.7826 &0.7609 &0.5109 &0.8587 &0.8142 &0.8587 &  \\
musk2 &0.8218 &0.7426 &0.6139 &0.7723 &0.7228 &0.6139 &0.7030 &0.7129 &0.6139 &0.6238 &\textbf{0.8756} &0.6733 &  \\
webmining &0.8500 &0.8142 &0.8142 &0.7699 &0.8142 &0.8142 &0.8407 &0.6903 &0.8142 &0.8142 &\textbf{0.9358} &0.8053 &  \\
trx &0.8860 &0.8964 &0.8705 &\textbf{0.9016} &0.8808 &0.8705 &0.8705 &0.8705 &0.8705 &0.8756 &0.6450 &0.8860 &  \\
mutagenesis-atoms &0.7714 &0.7606 &0.6649 &0.6436 &0.7074 &0.6649 &0.6915 &0.6649 &0.6649 &\textbf{0.7766} &\textbf{0.7766} &0.7606 &  \\
mutagenesis-bonds &0.8252 &0.7872 &0.6649 &0.6915 &0.7713 &0.6649 &0.7979 &0.6649 &0.6649 &0.8351 &0.8351 &\textbf{0.8564} &  \\
mutagenesis-chains &\textbf{0.8411} &0.7926 &0.6649 &0.6702 &0.7766 &0.6649 &0.8351 &0.6649 &0.6649 &0.8404 &0.8404 &0.8351 &  \\
tiger &0.7750 &0.7950 &0.5000 &0.5000 &0.7100 &0.5000 &0.7200 &0.7550 &0.5000 &0.6650 &\textbf{0.8000} &0.7250 &  \\
elephant &\textbf{0.8300} &\textbf{0.8300} &0.5000 &0.5000 &0.7900 &0.5000 &0.8100 &0.8000 &0.5000 &0.8000 &0.5625 &0.8250 &  \\
fox &0.6550 &0.6300 &0.5000 &0.5000 &0.5800 &0.5000 &0.5250 &0.4750 &0.5000 &0.6450 &\textbf{0.8587} &0.6500 &  \\
component &\textbf{0.9366} &0.9153 &0.8649 &0.8696 &0.8780 &0.8649 &0.8968 &0.8703 &0.8649 &0.9358 &0.6000 &0.9355 &  \\
function &0.9523 &0.9405 &0.9155 &0.9138 &0.9193 &0.9155 &0.9376 &0.9195 &0.9155 &\textbf{0.9649} &0.6238 &0.9647 &  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Average &\textbf{0.8264} &0.8010 &0.6390 &0.6886 &0.7279 &0.6390 &0.7724 &0.6883 &0.6390 &0.7598 &0.7598 &0.7550 &  \\
Rank &\textbf{2.2000} &3.8667 &9.6000 &7.8667 &6.5667 &9.6000 &5.3333 &8.5667 &9.6000 &4.7000 &4.8667 &5.2333 &  \\
\noalign{\smallskip}\hline
\end{tabular}}
\centering
\resizebox{0.95\textwidth}{!}{\begin{tikzpicture}
\draw (1,0) -- (11,0);
\foreach \x in {1,2,3,4,5,6,7,8,9,10,11} {
\draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
\ifthenelse{\x < 11}{\draw (\x+.5, 0) -- ++(0,.03);}{}
}

\coordinate (c0) at (2.2,0);
\coordinate (c1) at (3.8667,0);
\coordinate (c2) at (9.6,0);
\coordinate (c3) at (7.8667,0);
\coordinate (c4) at (6.5667,0);
\coordinate (c5) at (9.6,0);
\coordinate (c6) at (5.3333,0);
\coordinate (c7) at (8.5667,0);
\coordinate (c8) at (9.6,0);
\coordinate (c9) at (4.7,0);
\coordinate (c10) at (4.8667,0);
\coordinate (c11) at (5.2333,0);

\node (l0) at (c0) [below left=.01cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
\node (l1) at (c1) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
\node (l2) at (c2) [below left=.01cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
\node (l3) at (c3) [below left=.01cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
\node (l4) at (c4) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
\node (l5) at (c5) [above left=.25cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
\node (l6) at (c6) [above left=.25cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
\node (l7) at (c7) [above left=.25cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
\node (l8) at (c8) [below left=.16cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
\node (l9) at (c9) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
\node (l10) at (c10) [below left=.01cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
\node (l11) at (c11) [below right=.01cm and 0cm, align=left,scale=0.7] {\tiny Stacking};

\fill[fill=gray,fill opacity=0.5] (2.2,-0.1) rectangle (5.635,0.1);

\foreach \x in {0,1,2,3,4,5,6,7,8,9,10,11} {
\draw (l\x) -| (c\x);
};
\end{tikzpicture}}\vspace{-0.6em}
\captionof{figure}{Bonferroni-Dunn test for Accuracy}\label{fig:BonfDunnacc}\vspace{-0.5em}
\captionof{table}{Nemenyi, Holm, and Shaffer tests for Accuracy}\label{tab:statacc}
\scriptsize
\resizebox{0.95\textwidth}{!}{\begin{tabular}{lccccccccccc}
\noalign{\smallskip}\hline\noalign{\smallskip}
MIRSVM vs. &miGraph &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Holm $p$-value &0.0500 &0.0045 &0.0071 &0.0083 &0.0050 &0.0100 &0.0063 &0.0056 &0.0250 &0.0167 &0.0125 \\\noalign{\smallskip}\hline\noalign{\smallskip}
Wilcoxon $p$-value &0.0279 &0.0001 &0.0001 &0.0001 &0.0001 &0.0001 &0.0001 &0.0001 &0.0067 & $\geq$ 0.2 &0.0103 \\
Wilcoxon R$^+$ &98.500 &120.00 &119.00 &120.00 &120.00 &120.00 &120.00 &120.00 &106.00 &79.000 &104.00 \\
Wilcoxon R$^-$ &21.500 & 0.0000 &1.0000 & 0.0000 &0.0000 &0.0000 &0.0000 &0.0000 &14.000 &41.000 &16.000 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}}
\end{table}
Table~\ref{tab:accResults} shows the accuracy results of the $11$ algorithms over $15$ multi-instance datasets, along with their average and rank. The results indicate that the bag-based and ensemble learners perform better than the instance-based and wrapper methods. Specifically, MIRSVM achieves the best accuracy over $6$ of the $15$ datasets with a competitive average against the Bagging, Stacking, and TLC algorithms. Note that MIRSVM performs better than MISVM for all datasets, indicating that using representatives from each bag and limiting the number of support-vectors per negative bag improves the classification performance. The instance-level classifiers and wrapper methods, such as MIBoost, MIWrapper, and SimpleMI perform the worst. This behavior emphasizes the importance of not making prior assumptions about the positive bags' distributions.

@@

\begin{table}[H]
\caption{Precision}\label{tab:preResults}
\resizebox{0.95\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}ccccccccccccc}
\noalign{\smallskip}\hline\noalign{\smallskip}
Datasets &MIRSVM & miGraph & MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
\noalign{\smallskip}\hline\noalign{\smallskip}
suramin &0.7778 &0.7778 &\textbf{1.0000} &\textbf{1.0000} &0.2857 &\textbf{1.0000} &\textbf{1.0000} &0.5000 &\textbf{1.0000} &0.6429 &0.6514 &0.4000 &  \\
eastWest &0.7143 &0.7000 &0.5000 &0.8750 &0.5882 &0.5000 &0.7429 &\textbf{1.0000} &0.5000 &0.6053 &0.6053 &0.4444 &  \\
westEast &0.7272 &0.7273 &0.5000 &0.2727 &0.4600 &0.5000 &0.6939 &0.3600 &0.5000 &0.5581 &\textbf{0.9729} &0.6038 &  \\
musk1 &0.8519 &0.7778 &\textbf{1.0000} &0.9286 &0.9048 &\textbf{1.0000} &0.8049 &0.8108 &\textbf{1.0000} &0.8478 &0.8817 &0.8478 &  \\
musk2 &0.7059 &0.7826 &0.6139 &0.7826 &0.7576 &0.6139 &0.7424 &0.7538 &0.6139 &0.7400 &\textbf{0.9138} &0.7164 &  \\
webmining &0.7500 &\textbf{1.0000} &0.8142 &0.8173 &0.8142 &0.8142 &0.8936 &\textbf{1.0000} &0.8142 &0.8817 &0.9462 &0.8500 &  \\
trx &\textbf{1.0000} &0.8571 &0.8705 &0.9306 &0.9191 &0.8705 &0.8705 &0.8705 &0.8705 &0.9138 &0.6747 &0.9011 &  \\
mutagenesis-atoms &0.7872 &0.7985 &\textbf{1.0000} &0.4630 &0.6111 &\textbf{1.0000} &0.5439 &\textbf{1.0000} &\textbf{1.0000} &0.7059 &0.7059 &0.6667 &  \\
mutagenesis-bonds &0.8468 &0.8195 &\textbf{1.0000} &0.5385 &0.7500 &\textbf{1.0000} &0.6812 &\textbf{1.0000} &\textbf{1.0000} &0.7857 &0.7857 &0.8333 &  \\
mutagenesis-chains &0.8571 &0.8116 &\textbf{1.0000} &0.5091 &0.7059 &\textbf{1.0000} &0.7759 &\textbf{1.0000} &\textbf{1.0000} &0.7705 &0.7705 &0.7581 &  \\
tiger &0.7365 &0.7323 &0.5000 &0.5000 &0.6944 &0.5000 &0.7444 &0.7802 &0.5000 &0.6514 &\textbf{0.8000} &0.7320 &  \\
elephant &0.8576 &\textbf{0.8750} &0.5000 &0.5000 &0.7959 &0.5000 &0.8444 &0.7679 &0.5000 &0.8000 &0.5581 &0.8283 &  \\
fox &0.6040 &0.6275 &0.5000 &0.5000 &0.5833 &0.5000 &0.5287 &0.4854 &0.5000 &0.6747 &\textbf{0.8478} &0.6705 &  \\
component &\textbf{0.9866} &0.7782 &0.8649 &0.8778 &0.8902 &0.8649 &0.8958 &0.8696 &0.8649 &0.9462 &0.6429 &0.9449 &  \\
function &0.8459 &0.6775 &0.9155 &0.9202 &0.9317 &0.9155 &0.9376 &0.9197 &0.9155 &\textbf{0.9729} &0.7400 &0.9726 &  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Average &0.8033 &0.7828 &0.7719 &0.6944 &0.7128 &0.7719 &0.7800 &\textbf{0.8079} &0.7719 &0.7665 &0.7665 &0.7447 &  \\
Rank &\textbf{5.3333} &6.1333 &7.1000 &7.3333 &7.3667 &7.1000 &5.8667 &5.8667 &7.1000 &5.9000 &6.3333 &6.5667 &  \\
\noalign{\smallskip}\hline
\end{tabular}}
\centering
\resizebox{0.95\textwidth}{!}{\begin{tikzpicture}
\draw (3,0) -- (12,0);
\foreach \x in {3,4,5,6,7,8,9,10,11,12} {
\draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
\ifthenelse{\x < 12}{\draw (\x+.5, 0) -- ++(0,.03);}{}
}

\coordinate (c0) at (5.3333,0);
\coordinate (c1) at (6.1333,0);
\coordinate (c2) at (7.1,0);
\coordinate (c3) at (7.3333,0);
\coordinate (c4) at (7.3667,0);
\coordinate (c5) at (7.1,0);
\coordinate (c6) at (5.8667,0);
\coordinate (c7) at (5.8667,0);
\coordinate (c8) at (7.1,0);
\coordinate (c9) at (5.9,0);
\coordinate (c10) at (6.3333,0);
\coordinate (c11) at (6.5667,0);

\node (l0) at (c0) [below left=.01cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
\node (l1) at (c1) [below right=.16cm and 0cm, align=left,scale=0.7] {\tiny miGraph};
\node (l2) at (c2) [above right=.05cm and 0cm, align=left,scale=0.7] {\tiny MIBoost};
\node (l3) at (c3) [below right=.17cm and 0cm, align=left,scale=0.7] {\tiny MIOptimalBall};
\node (l4) at (c4) [below right=.01cm and 0cm, align=left,scale=0.7] {\tiny MIDD};
\node (l5) at (c5) [above right=.15cm and 0cm, align=left,scale=0.7] {\tiny MIWrapper};
\node (l6) at (c6) [below left=.1cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
\node (l7) at (c7) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
\node (l8) at (c8) [above right=.3cm and 0cm, align=left,scale=0.7] {\tiny SimpleMI};
\node (l9) at (c9) [above left=.24cm and 0cm, align=right,scale=0.7] {\tiny TLC};
\node (l10) at (c10) [below right=.01cm and 0cm, align=left,scale=0.7] {\tiny Bagging};
\node (l11) at (c11) [above left=.24cm and 0cm, align=right,scale=0.7] {\tiny Stacking};

\fill[fill=gray,fill opacity=0.5] (5.3333,-0.1) rectangle (8.7683,0.1);

\foreach \x in {0,1,2,3,4,5,6,7,8,9,10,11} {
\draw (l\x) -| (c\x);};
\end{tikzpicture}}\vspace{-1.1em}
\captionof{figure}{Bonferroni-Dunn test for Precision}\label{fig:BonfDunnprec}\vspace{-0.5em}
\captionof{table}{Nemenyi, Holm, and Shaffer tests for Precision}\label{tab:statprec}
\scriptsize
\resizebox{0.95\textwidth}{!}{\begin{tabular}{lccccccccccc}
\noalign{\smallskip}\hline\noalign{\smallskip}
MIRSVM vs. &miGraph &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Holm $p$-value &0.0125 &0.0056 &0.0050 &0.0045 &0.0063 &0.0250 &0.0500 &0.0071 &0.0167 &0.0100 &0.0083 \\\noalign{\smallskip}\hline\noalign{\smallskip}
Wilcoxon $p$-value & $\geq$ 0.2 & $\geq$ 0.2 &0.0946 &0.0256 & $\geq$ 0.2 & $\geq$ 0.2 & $\geq$ 0.2 & $\geq$ 0.2 &0.1354 & $\geq$ 0.2 &0.1354 \\
Wilcoxon R$^+$ &75.000 &71.000 &90.000 &99.000 &71.000 &75.000 &55.000 &71.000 &87.000 &74.000 &87.000 \\
Wilcoxon R$^-$ &45.000 &49.000 &30.000 &21.000 &49.000 &45.000 &65.000 &49.000 &33.000 &46.000 &33.000 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}}
\captionof{table}{Recall}\label{tab:recResults}
\resizebox{0.95\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}ccccccccccccc}
\noalign{\smallskip}\hline\noalign{\smallskip}
Datasets &MIRSVM & miGraph & MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
\noalign{\smallskip}\hline\noalign{\smallskip}
suramin &\textbf{1.0000} &\textbf{1.0000} &0.0000 &0.4500 &0.1000 &0.0000 &0.4500 &0.5000 &0.0000 &0.4500 &0.7100 &0.3333 &  \\
eastWest &\textbf{1.0000} &0.7000 &0.7000 &0.5250 &0.7500 &0.7000 &0.6500 &0.1250 &\textbf{1.0000} &0.5750 &0.5750 &0.4000 &  \\
westEast &0.8000 &0.8000 &0.9000 &0.1500 &0.5750 &0.9000 &0.8500 &0.2250 &\textbf{1.0000} &0.6000 &0.9892 &0.8000 &  \\
musk1 &\textbf{0.9787} &0.8936 &0.0000 &0.5778 &0.8444 &0.0000 &0.7333 &0.6667 &0.0000 &0.8667 &0.8913 &0.8667 &  \\
musk2 &0.9231 &0.4615 &\textbf{1.0000} &0.8710 &0.8065 &\textbf{1.0000} &0.7903 &0.7903 &\textbf{1.0000} &0.5968 &0.9464 &0.7742 &  \\
webmining &0.2857 &0.0000 &\textbf{1.0000} &0.9239 &\textbf{1.0000} &\textbf{1.0000} &0.9130 &0.6196 &\textbf{1.0000} &0.8913 &0.9815 &0.9239 &  \\
